Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-29 ms.tex
separate out sentences explaining 3000 GHz color correction
more clean-up of color correction discussion

Here $\nu_{i,c}$ is the nominal band center frequency of band $\nu_i$,  with 
$\nu_{i,c} \in$ \{100, 143, 217, 353, 545, 857, 3000\} GHz. 
$\mathcal{T}_{\nu_i}(\nu)$ represents the relative transmission as a function 
of frequency for band $\nu_i$. For the HFI maps, $\mathcal{T}_{\nu_i}(\nu)$ is 
given by the \PLANCK~transmission curves provided in the file 
\verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. For 3000 GHz, we have 
adopted the DIRBE transmission curve. These bandpass correction factors 
are applied in the sense that $b_{\nu_i}(T ,\beta)\times M_{\nu_{i,c}}$ 
is a prediction suitable for comparison to the \PLANCK~data products.

The broadband, two-component model prediction in band $\nu_i$, termed 
$\tilde{I}_{\nu_i}$, is then constructed as a linear combination of 
color-corrected MBB terms:

\begin{equation} \label{equ:broadband}
\tilde{I}_{\nu_i} \propto \sum_{k=1}^{2} b_{\nu_i}(T_k, \beta_k) f_k q_k (\nu_{i,c}/\nu_0)^{\beta_k} B_{\nu_{i,c}}(T_k)
\end{equation}

Note that, as in FDS99, $f_2$=(1$-$$f_1$) by convention. This finite bandpass 
correction approach allows us to predict the \textit{broadband} measurement 
$\tilde{I}_{\nu_i}$ by computing monochromatic flux densities at the central 
frequency $\nu_{i,c}$ and then multiplying by factors $b_{\nu_i}(T, \beta)$ 
which are interpolated off of a set of precomputed, one-dimensional lookup 
tables each listing $b_{\nu_i}(T, \beta)$ as a function of $T$. We avoided the 
need to interpolate in both $\beta$ and $T$ by computing only a small set of 
one dimensional correction factors for the particular set of $\beta$ values of 
interest ($\beta \in$ \{1.67, 2.7, 1.19, 2.61\}, see Table \ref{tab:global}).

This finite bandpass correction approach makes the MCMC sampling described in 
$\S$\ref{sec:mcmc} much more computationally efficient by circumventing the 
need to perform the integral in the numerator of Equation \ref{equ:bpcorr} 
on-the-fly for each proposed dust temperature. We have chosen to compute the 
bandpass corrections on a per-MBB basis because this approach is very 
versatile; all possible two-component models are linear combinations of MBBs, 
so we can apply all of our finite bandpass machinery even when we allow 
parameters other than temperature (e.g. $f_1$) to vary and thereby change the 
dust spectrum shape.

@@

This equation is quite similar to Equation \ref{equ:broadband}, but with two 
important differences. First, the normalization of $\tilde{I}_{\nu_i}$ is now 
specified by $\tilde{I}_{545}$, which represents the broadband intensity 
measured in the \PLANCK~545 GHz band. The denominator serves to ensure that,
for the case of $\nu_i$=545 GHz, $\tilde{I}_{545}$ is self-consistent. Second, 
each term in the numerator is multiplied by a conversion factor 
$u_{\nu_i}^{-1}(T_k, \beta_k)$. This factor is necessary because some of the 
\PLANCK~maps of interest have units of $K_{CMB}$ (100-353 GHz), while the
remaining maps (545-3000 GHz) have units of MJy/sr. Complicating matters, the 
conversion from $K_{CMB}$ to MJy/sr depends on the spectrum under 
consideration; attempting to apply conversion factors to put all of the 
observed maps themselves into common units is not a particularly attractive 
option. Therefore, we adopt the strategy of predicting each band in its native 
units, whether MJy/sr or $K_{CMB}$. For this reason, we always evaluate 
$B_{\nu_{i,c}}$ in Equation \ref{eqn:inten} in MJy/sr and let $u_{\nu_i}$=1 
(dimensionless) for all $\nu_i$$\ge$545 GHz. For $\nu_i$$\le$353 GHz, 
$u_{\nu_i}(T_k, \beta_k)$ represents the appropriate conversion factor from 
$K_{CMB}$ to MJy/sr:

>>>>

Here $\nu_{i,c}$ is the nominal band center frequency of band $\nu_i$,  with 
$\nu_{i,c} \in$ \{100, 143, 217, 353, 545, 857, 3000\} GHz. 
$\mathcal{T}_{\nu_i}(\nu)$ represents the relative transmission as a function 
of frequency for band $\nu_i$. For the HFI maps, $\mathcal{T}_{\nu_i}(\nu)$ is 
given by the \PLANCK~transmission curves provided in the file 
\verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. These bandpass correction 
factors are applied in the sense that $b_{\nu_i}(T ,\beta)\times M_{\nu_{i,c}}$
is a prediction suitable for comparison to the \PLANCK~data products.

For 3000 GHz, we have adopted the DIRBE transmission curve. Since DIRBE-quoted
fluxes also follow the $\alpha$=$-1$ convention, Equation \ref{equ:bpcorr}
remains applicable.

The two-component model prediction in band $\nu_i$ under the IRAS convention, 
termed $\tilde{I}_{\nu_i}$, is then constructed as a linear combination of 
color-corrected MBB terms:

\begin{equation} \label{equ:iras}
\tilde{I}_{\nu_i} \propto \sum_{k=1}^{2} b_{\nu_i}(T_k, \beta_k) f_k q_k (\nu_{i,c}/\nu_0)^{\beta_k} B_{\nu_{i,c}}(T_k)
\end{equation}

Note that, as in FDS99, $f_2$=(1$-$$f_1$) by convention. Our color correction 
approach allows us to predict $\tilde{I}_{\nu_i}$ by computing monochromatic 
flux densities at the central frequency $\nu_{i,c}$ and then multiplying by 
factors $b_{\nu_i}(T, \beta)$ which are interpolated off of a set of 
precomputed, one-dimensional lookup tables each listing $b_{\nu_i}(T, \beta)$ 
as a function of $T$. We avoided the need to interpolate in both $\beta$ and 
$T$ by computing only a small set of one dimensional correction factors for the
particular set of $\beta$ values of interest 
($\beta \in$ \{1.67, 2.7, 1.19, 2.61\}, see Table \ref{tab:global}).

% need some sort of clarification about the fact that, in the parts of the 
% analysis where beta floats, this precomputation/interpolation is NOT 
% what we do

This color correction approach makes the MCMC sampling described in 
$\S$\ref{sec:mcmc} much more computationally efficient by circumventing the 
need to perform the integral in the numerator of Equation \ref{equ:bpcorr} 
on-the-fly for each proposed dust temperature. We have chosen to compute the 
color corrections on a per-MBB basis because this approach is very 
versatile; all possible two-component models are linear combinations of MBBs, 
so we can apply all of our color correction machinery even when we allow 
parameters other than temperature (e.g. $f_1$) to vary and thereby change the 
dust spectrum shape.

@@

This equation is quite similar to Equation \ref{equ:iras}, but with two 
important differences. First, the normalization of $\tilde{I}_{\nu_i}$ is now 
specified by $\tilde{I}_{545}$, which represents the broadband intensity 
measured in the \PLANCK~545 GHz band. The denominator serves to ensure that,
for the case of $\nu_i$=545 GHz, $\tilde{I}_{545}$ is self-consistent. Second, 
each term in the numerator is multiplied by a conversion factor 
$u_{\nu_i}^{-1}(T_k, \beta_k)$. This factor is necessary because some of the 
\PLANCK~maps of interest have units of $K_{CMB}$ (100-353 GHz), while the
remaining maps (545-3000 GHz) have units of MJy/sr. Complicating matters, the 
conversion from $K_{CMB}$ to MJy/sr depends on the spectrum under 
consideration; attempting to apply conversion factors to put all of the 
observed maps themselves into common units is not a particularly attractive 
option. Therefore, we adopt the strategy of predicting each band in its native 
units, whether MJy/sr or $K_{CMB}$. For this reason, we always evaluate 
$B_{\nu_{i,c}}$ in Equation \ref{eqn:inten} in MJy/sr and let $u_{\nu_i}$=1 
(dimensionless) for all $\nu_i$$\ge$545 GHz. For $\nu_i$$\le$353 GHz, 
$u_{\nu_i}(T_k, \beta_k)$ represents the appropriate conversion factor from 
$K_{CMB}$ to MJy/sr:
